The galactic chemical evolution of carbon: Constraining stellar nucleosynthesis

### 2023-05-19 out/paper_old/tex/main.tex
multithread options back and reorginization

\newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
\newcommand{\Ycc}{\ensuremath{Y_{\rm C}^{\rm cc}}}
\newcommand{\Yct}{\ensuremath{Y_{\rm C, 0}^{\rm tot}}}
\newcommand{\Yoc}{\ensuremath{Y_{\rm O}^{\rm cc}}}
\newcommand{\Ycagb}{\ensuremath{Y_{\rm C}^{\rm agb}}}

@@

\begin{figure*}
    \centering
    \includegraphics[]{subgiants_mgh.pdf}
    \includegraphics[]{subgiants_mgfe.pdf}
    \caption{Chemical abundance relationships of our sample of APOGEE subgiants (see Jack et al. 2023). Left panel shows }
    \label{fig:subgiants}
\end{figure*}
\section{Nucleosynthesis}

@@

\begin{figure*}
\label{fig:c_evo}
\includegraphics{evo_tracks-9.pdf}
\includegraphics{evo_slices-2.pdf}
\caption{The top set of panes show the time evolution of the gas phase of our
    fiducial model, plotted as tracks through \caah and \caafe where each colored line corresponds to the evolution at that galactic radius. 
The bottom set instead shows the galaxies gas-phase \caah and \caafe trend at 5 different time slices. 
}
\end{figure*}

@@

\begin{figure*}
\includegraphics[scale=0.6]{oob_agb-1.pdf}

@@

\begin{figure*}\label{fig:beta_f}
\includegraphics[scale=0.6]{beta-1.pdf}
\includegraphics[scale=0.6]{f_agb-1.pdf}

@@

@@

\begin{figure*}
\includegraphics[scale=0.6]{lateburst_eta-1.pdf}

@@

\begin{figure}
    \includegraphics[scale=0.6]{cooh_scatter.pdf}
    \caption{The simulated stars of our model at present day plotted on \caah~and colored such that lighter colors represent stars born at greater galactric radii.}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=0.6]{cnoh.pdf}
    \caption{Caption}
    \label{fig:cnofe}
\end{figure}

@@

In the first panel, both V13 and the subgiant sample predict similar trends in [C/Mg]-[Mg/H] but there appears to be a systematic offset of about 0.2dex. Reproducing the trend is promising as V21's mixing corrections were metallicity-dependent so the uncorrected sample of APOGEE giants does not match the subgiant trend.

The systematic offset could be explained by overpredicting the effects of FDU or other *** in V21's stellar evolution models??? or other subgiant physics???

In the second panel, agreement appears to be better. Both the MDF and the slope are nearly identical,
There is a slight deviation in slope between the models, and this could again be a systematic such as underestimation of **8some stellar effect**** at higher metallicities.

We compare both of **** in Fig. \ref{fig:fiorenzo_jack}.

\begin{figure*}
    \centering
    \includegraphics[scale=0.5]{fiorenzo_vs_jack_c-1.pdf}
    \includegraphics[scale=0.5]{fiorenzo_vs_jack_n-1.pdf}
    \caption{A comparison of estimated stellar birth abundance trends from the subgiant sample and
        \citet{fiorenzo+21}
    }
    \label{fig:fiorenzo_jack}
\end{figure*}

>>>>

\newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
\newcommand{\Ycc}{\ensuremath{y_{\rm C}^{\rm cc}}}
\newcommand{\Yct}{\ensuremath{y_{\rm C, 0}^{\rm tot}}}
\newcommand{\Yoc}{\ensuremath{y_{\rm O}^{\rm cc}}}
\newcommand{\Ycagb}{\ensuremath{y_{\rm C}^{\rm agb}}}

@@

\begin{figure*}
    \centering
    \includegraphics[]{subgiants_mgh.pdf}
    \includegraphics[]{subgiants_mgfe.pdf}
    \caption{The [C/Mg] ratio against [Mg/H] (left) and [Mg/Fe] (right). The left panel uses blue and orange to represent high and low $\alpha$ sequences respectively. On the right, we plot more metal rich ([Mh/H]) stars with darker colors.}
    \label{fig:subgiants}
\end{figure*}
\section{Nucleosynthesis}

@@

\begin{figure*}
\label{fig:c_evo}
\includegraphics{evo_tracks.pdf}
\includegraphics{evo_slices.pdf}
\caption{The top set of panes show the time evolution of the gas phase of our
    fiducial model, plotted as tracks through \caah and \caafe where each colored line corresponds to the evolution at that galactic radius. 
The bottom set instead shows the galaxies gas-phase \caah and \caafe trend at 5 different time slices. 
}
\end{figure*}

@@

\begin{figure*}
\includegraphics[]{oob_agb.pdf}

@@

\begin{figure*}\label{fig:beta_f}
\includegraphics{beta.pdf}
\includegraphics{f_agb.pdf}

@@

One caveat is that the slope of this trend is also determined by the ratio of delayed iron to CCSNe iron production as well. If the SNeIa iron fraction is increased, then more iron enters later reducing the slope of the trend as AGB becomes a more rapid mechanism than Fe comparatively. The difference however is that changing the Fe franction mostly affects the tail of the distribution as this controls the speed of descent off the high $\alpha$ sequence, but the AGB fraction even changes the behavior for the low $\alpha$ sequence.

@@

\begin{figure*}
\includegraphics[]{lateburst_eta.pdf}

@@

\begin{figure*}
    \includegraphics[scale=0.9]{cooh_scatter.pdf}
    \includegraphics[scale=0.9]{cnoh_scatter.pdf}
    \caption{The simulated stars of our model at present day plotted on \caah~and colored such that lighter colors represent stars born at greater galactric radii.}
\end{figure*}

@@
